XSGRB - The X-shooter GRB afterglow sample

### 2017-09-18 document/XSGRB_sample.tex
Trimming sections

A fraction of the bursts presented here \todo{Insert exact
number} have already had their hosts investigated in \citet{Kruhler2015}, for
which extractions of the hosts exist. The focus of the data presented here are
on the afterglows themselves and in the absence of a clear afterglow, the host.
We will not, however, investigate the hosts.

@@

For all earth-based telescopes, the light of interest has to pass through Earths
atmosphere, where the atmospheric content and conditions make an imprint on the
received spectrum. These telluric features can be calculated in a multitude of
ways and we employ a prioritized list of methods here, depending on the
availability of the different method. Since the observation are often taken at
odd times under varying conditions, this prioritized list ensures that we are
always doing the optimal correction.

The highest priority method is using the GRB afterglow continuum itself, where
the atmospheric conditions have directly been imprinted on the spectrum. The
telluric features can directly be fit with an atmospheric model
\citep{Smette2015, Kausch2015}, which can then be used to correct for the absorption. The accuracy of the correction depends on the 
The requirement here is that the afterglow continuum spectrum has a
signal-to-noise higher than a value of 10.

@@

%As is shown in Sect. \ref{timing}, the redshift completeness
%decreases with increasing follow-up delay, we can additionally increase the
%redshift completeness by imposing cuts on the follow-up delay. Our ability to
%rapidly follow up a burst is also not dependent on the burst properties and
%therefore we can additionally cut delays longer than 24 hours (all burst in the
%sample are in principle observable within 24 hours).

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Redshifts}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

The biased introduced in the redshift distribution by the increased ability to
secure redshift of optically brighter bursts has been investigated by
\citet{Turpin2016} which find that we systematically find redshift for longer
GRBs. Additionally only the brightest GRBs are seen above redshift $z \gtrsim
1$. \todo{Additional text}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Afterglow-based redshifts}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Emissionline-based redshifts}	
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Redshift completeness

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\subsection{X-ray column densities vs. optically derived ones}	
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%	
%
%\begin{figure}
%	\centerline{\includegraphics[width=10cm]{figures/OAXR_NH_sphere.pdf}}
%	\caption{Optically derived HI column densities vs. X-ray derived ones taken from \citet{Buchner2016}. The colors of the points reflect the redshift of the burst. Circles mark the column densities published in \citet{Fynbo2009} and squares mark the ones derived as part of the sample presented here. Overplot in blue is the 1:1 correspondence, expected if the conditions local to the GRBs are similar to the local ISM abundances. If the metallicity is lower at the GRB site, the point move upwards in the plot. }
%	\label{fig:OAXR}
%\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Why is the HI column truncated?}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

What is the expected transmission for a high-column HI, where the hydrogen primarily will be in the form of H2? Number of bursts with detected H2 and their HI column density. Rahmati Schaye, Krongold Prochaska.

>>>>

%A fraction of the bursts presented here \todo{Insert exact
%number} have already had their hosts investigated in \citet{Kruhler2015}, for
%which extractions of the hosts exist. The focus of the data presented here are
%on the afterglows themselves and in the absence of a clear afterglow, the host.
%We will not, however, investigate the hosts.

@@

For all earth-based telescopes, the light of interest has to pass through Earths
atmosphere, where the atmospheric content and conditions make an imprint on the
received spectrum. These telluric features can be corrected for in a multitude
of ways. We employ a prioritized list of methods here, depending on the
availability of the different method. Since the observation are often taken at
odd times under varying conditions, this prioritized list ensures that we are
always doing the optimal correction.

The highest priority method is using the GRB afterglow continuum itself, where
the atmospheric conditions have directly been imprinted on the spectrum. The
telluric features can directly be fit with an atmospheric model
\citep{Smette2015, Kausch2015}, which can then be used to correct for the
absorption. The accuracy of the correction depends on the S/N for the target
spectrum, where we have chosen the requirement that the afterglow continuum
spectrum has a median signal-to-noise higher than a value of 10.

@@

As is shown in Sect. \ref{timing}, the redshift completeness
decreases with increasing follow-up delay, we can additionally increase the
redshift completeness by imposing cuts on the follow-up delay. Our ability to
rapidly follow up a burst is also not dependent on the burst properties and
therefore we can additionally cut delays longer than 24 hours (all burst in the
sample are in principle observable within 24 hours). \todo{Unfinished section}

The biased introduced in the redshift distribution by the increased ability to
secure redshift of optically brighter bursts has been investigated by
\citet{Turpin2016} which find that we systematically find redshift for longer
GRBs. Additionally only the brightest GRBs are seen above redshift $z \gtrsim
1$. \todo{Unfinished section}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\subsection{X-ray column densities vs. optically derived ones (Remove section)}	
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%	
%
%\begin{figure}
%	\centerline{\includegraphics[width=10cm]{figures/OAXR_NH_sphere.pdf}}
%	\caption{Optically derived HI column densities vs. X-ray derived ones taken from \citet{Buchner2016}. The colors of the points reflect the redshift of the burst. Circles mark the column densities published in \citet{Fynbo2009} and squares mark the ones derived as part of the sample presented here. Overplot in blue is the 1:1 correspondence, expected if the conditions local to the GRBs are similar to the local ISM abundances. If the metallicity is lower at the GRB site, the point move upwards in the plot. }
%	\label{fig:OAXR}
%\end{figure}	
%	
%	
%	
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\subsection{Why is the HI column truncated? (Remove section)}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%What is the expected transmission for a high-column HI, where the hydrogen primarily will be in the form of H2? Number of bursts with detected H2 and their HI column density. Rahmati Schaye, Krongold Prochaska.
